Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-12-19 Manuscript/manuscript.tex
Small edits in the Results-first paragraph (added refs)

We compared X-ray scattering form factors and NMR order parameters of bilayers
in pure water without any ions (or only counter ions)
from simulations and experiments
as the first step in the assessment of the quality of the model. 
The experimental X-ray scattering form factors 
of a bilayer are well reproduced  
(see Fig.~\ref{simVSexpNOions_POPS}).

>>>>

We compared X-ray scattering form factors and NMR order parameters of bilayers
in pure water without any ions (or only counter ions)
from simulations and experiments. 
The experimental X-ray scattering form factors 
of a bilayer are well reproduced by ECC-POPS, 
while for Lipid17/Dang they are in a slight disagreement
(see Fig.~\ref{simVSexpNOions_POPS}). 
The agreement of Lipid17 can be improved by using different parametes for ions \cite{aqvist90},
which, however, bring other kinds of artifacts with them 
(e.g., incorrect pairing of ions, condensation at larger salt concentrations \cite{kohagen16, chen07}).
